### 2024-01-16 ms.qmd
Updates

In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig. @FigMethods B). The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour. We placed the food reward (small, frozen, *A. domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp. The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals. The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour preference that could bias our results, we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. Lizards were tested in this task once a day for 35 days.

@@

```{r, InterceptsRev}
```

@@

  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #Tor order the columns in the way I want for the table

@@

>>>>

In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig. @FigMethods B). The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour. We placed the food reward (small, frozen, *A. domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp. The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals. The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour preference that could bias our results (see Supplementary Material), we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. Lizards were tested in this task once a day for 35 days.

@@

@@

  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table

@@

## Suplementary Material

### Colour preference in the Associative task
To test if lizards were biased towards blue as our preliminary analyses indicated, we employed the intercept estimates from our posterior distribution. We get this intercepts for each species, group and treatment, and we estimated the probability of choosing right using the formula:

As we used the link=‘logit’ adjustment in our initial models.
```{r, Tablebias}
#| label: Tablebias
#| tbl-cap: "Biases"
# First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
## 1) L. delicata
### Group = red
probright_drCORTCold <- 1/(1+exp(-deli_asso_red$b_Intercept))
probright_drControlCold <- 1/(1+exp(-(deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)))
probright_drCORTHot <- 1/(1+exp(-(deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
probright_drControlHot <- 1/(1+exp(-(deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
### Group = blue
probright_dbCORTCold <- 1/(1+exp(-(deli_asso_blue$b_Intercept)))
probright_dbControlCold <- 1/(1+exp(-(deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)))
probright_dbCORTHot <- 1/(1+exp(-(deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
probright_dbControlHot <- 1/(1+exp(-(deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
## 2) L. guichenoti
### Group = red
probright_grCORTCold <- 1/(1+exp(-guich_asso_red$b_Intercept))
probright_grControlCold <- 1/(1+exp(-(guich_asso_red$b_cortControl + guich_asso_red$b_Intercept)))
probright_grCORTHot <- 1/(1+exp(-(guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
probright_grControlHot <- 1/(1+exp(-(guich_asso_red$'b_cortControl:tempHot' + guich_asso_red$b_cortControl + guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
### Group = blue
probright_gbCORTCold <- 1/(1+exp(-guich_asso_blue$b_Intercept))
probright_gbControlCold <- 1/(1+exp(-(guich_asso_blue$b_cortControl + guich_asso_blue$b_Intercept)))
probright_gbCORTHot <- 1/(1+exp(-(guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
probright_gbControlHot <- 1/(1+exp(-(guich_asso_blue$'b_cortControl:tempHot' + guich_asso_blue$b_cortControl + guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
# Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
prob_df <- data.frame(
  probright_drCORTCold = probright_drCORTCold,
  probright_drControlCold = probright_drControlCold,
  probright_drCORTHot = probright_drCORTHot,
  probright_drControlHot = probright_drControlHot,
  probright_dbCORTCold = probright_dbCORTCold,
  probright_dbControlCold = probright_dbControlCold,
  probright_dbCORTHot = probright_dbCORTHot,
  probright_dbControlHot = probright_dbControlHot,
  probright_grCORTCold = probright_grCORTCold,
  probright_grControlCold = probright_grControlCold,
  probright_grCORTHot = probright_grCORTHot,
  probright_grControlHot = probright_grControlHot,
  probright_gbCORTCold = probright_gbCORTCold,
  probright_gbControlCold = probright_gbControlCold,
  probright_gbCORTHot = probright_gbCORTHot,
  probright_gbControlHot = probright_gbControlHot
) %>% #This way we get a df with 16 variables
  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
  gather(key = "column", value = "value", .) %>% #To transpose the df
  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
  mutate(Group = gsub(".*_(dr|db|gr|gb).*", "\\1",column)) %>%
  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
  mutate(Treatment = factor(Treatment, 
                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
                levels = c("d", "g"),
                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
  mutate(Group = recode(Group, "dr" = "Red", "db" = "Blue", "gr" = "Red", "gb" = "Blue")) %>%
  pivot_wider(names_from = Group, values_from = c(value, column)) %>% #To split the df in Red and Blue
data.frame()

write.csv(prob_df, file= "./output/Checking/prob_df.csv")

# Then we build a df with the statistical comparison between probabilities (Blue minus Red) for each treatment and species and p-values for each comparison
comp_prob <- data.frame(
  (probright_dbCORTCold - probright_drCORTCold),
  (probright_dbControlCold - probright_drControlCold),
  (probright_dbCORTHot - probright_drCORTHot),
  (probright_dbControlHot - probright_drControlHot),
  (probright_gbCORTCold - probright_grCORTCold),
  (probright_gbControlCold - probright_grControlCold),
  (probright_gbCORTHot - probright_grCORTHot),
  (probright_gbControlHot - probright_grControlHot)
) %>% 
  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
  gather(key = "column", value = "value", .) %>% #To transpose the df
  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
  mutate(Treatment = factor(Treatment, 
                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
                levels = c("d", "g"),
                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
  rename("[Blue - Red]" = "value") %>%
data.frame()
comp_pval <- data.frame(
  pmcmc(probright_dbCORTCold - probright_drCORTCold),
  pmcmc(probright_dbControlCold - probright_drControlCold),
  pmcmc(probright_dbCORTHot - probright_drCORTHot),
  pmcmc(probright_dbControlHot - probright_drControlHot),
  pmcmc(probright_gbCORTCold - probright_grCORTCold),
  pmcmc(probright_gbControlCold - probright_grControlCold),
  pmcmc(probright_gbCORTHot - probright_grCORTHot),
  pmcmc(probright_gbControlHot - probright_grControlHot)
) %>% 
  summarise_all(.funs = mean) %>% #This way we get a df with 16 variables and 1 row
  gather(key = "column", value = "value", .) %>% #To transpose the df
  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
  mutate(Treatment = factor(Treatment, 
                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
                    labels = c("CORTCold"="CORT-Cold", "ControlCold"="Control-Cold", "CORTHot"="CORT-Hot", "ControlHot"="Control-Hot"))) %>%
                levels = c("d", "g"),
                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
  rename("p-value" = "value") %>%
data.frame()
#Create the final database and the table
table_df <- merge(prob_df, comp_prob, by = c("Specie", "Treatment")) %>%
  merge(comp_pval, by = c("Specie", "Treatment")) %>%
  select(Specie, Treatment, value_Blue, value_Red, X.Blue...Red., p.value) %>%
  mutate(Treatment = factor(Treatment, 
data.frame()
table_df <- table_df %>%
colour_table <- flextable(table_df) %>%
  bold(~ `p.value` < 0.05, ~ `p.value` + X.Blue...Red.) %>%
  set_header_labels(value_Blue = "Blue",
                    value_Red = "Red",
                    p.value = "p-value",
                    X.Blue...Red. = "[Blue - Red]") %>%
  colformat_num(columns = c("Blue", "Red", "[Blue-Red]", "p-value"), digits = 3) %>% # To set the number of decimals
  flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
  hline(i = c(4), j = c(1:6), part = "body") %>% # To make some horizontal lines
colour_table

For _L. delicata_, there was no differences between treatments ('Red' group: 'Control-Cold' - 'CORTCold')
